Normalization Circularity in Population-Based FA Analysis

### 2011-06-07 ANTsTBSS/paper.tex
ENH: minor changes + important discussion points

After creation of the simulated data set, we performed voxelwise testing (both $t$-testing
and Wilcoxon rank-sum testing, one-tailed, $\alpha = 0.95$) with false discovery
rate correction within the white matter to get ``true'' cumulative distribution functions (cdfs).  The cdf vertical axis shows the cumulative number of voxels with corrected p-values at or below a given significance level (horizontal axis) and thus may be used as a surrogate measure for spatial sensitivity.  From here, we denote these graphs as "statistical significance curves."  These curves are plotted in black in Fig. \ref{fig:simulated_testing}.  To illustrate the 
effect of similarity metric on statistical significance, we performed ANTs registration \cite{Avants2011} of each subject to the template
(Fig. \ref{fig:simulated_data}(b)) using cross correlation (CC), mutual information (MI), 
Demons \cite{Thirion1998}, and sum of squared differences (SSD). A representative deformed image
using the SSD metric and its corresponding deformed grid is given in 
Fig. \ref{fig:simulated_data_warped}. 
The resulting statistical significance curves are plotted with the true significance curves in Fig. 
\ref{fig:simulated_testing}.

@@

\subsection{Anatomical Image Template Construction}

An important step in reducing intersubject variability is
normalization to a standardized coordinate system for
cross-population comparison.  Various approaches
exist for determination of the normalized space such as selection of a
pre-existing template based on a single subject, e.g. the Talairach atlas \cite{Talairach1988}), or 
a publicly available averaged group of subjects, e.g. the MNI \cite{Collins1994} or 
ICBM \cite{Mazziotta1995} templates.

Recent trends, however, indicate a growing popularity of generating population-specific 
templates for minimizing potential confounds.  This includes the
diffeomorphic approach of Joshi et al. who employ the SSD metric and a shape 
distance to bring the subject group of images into alignment \cite{Joshi2004}.  Variants
include extension to multiple modalities \cite{Lorenzen2006} and small deformations
\cite{Geng2009}.  These approaches iteratively minimize group difference in ``congealing''
towards a representative image template \cite{Learned-Miller2006}.

In contrast, Avants et al. explicitly model the geometric component of the 
normalized space during optimization.  Coupling the intrinsic symmetry of 
SyN pairwise registration \cite{Avants2011} and an
optimized sharpening/averaging of the template appearance, Symmetric Group
Normalization (SyGN) is a powerful framework for producing optimal population-specific
templates \cite{Avants2010}. Given a set of representative images, 
$\{I_1, I_2, \ldots, I_M\}$, optimization involves finding the set of paired
diffeomorphic transformations, $\left\{\left(\phi^1_1, \phi^1_2\right), 
\left(\phi^2_1, \phi^2_2\right), \ldots, \left(\phi^M_1, \phi^M_2\right) \right\}$,
the optimal template appearance, $J^*$, and corresponding coordinate system, $\psi(\mathbf{x})$,
which minimize the following cost function:
\begin{align}
  \sum_{m=1}^M \left[
    D\left( \psi(\mathbf{x}), \phi^m_1(\mathbf{x}, 1) \right) + 
    \Pi \left( I_m\left(\phi^m_2(\mathbf{x}, 0.5) \right), J^*\left(\phi^m_1(\mathbf{x}, 0.5) \right) \right)
    \right]
\end{align}
where $D$ is the diffeomorphic shape distance, 
\begin{align}
  D\left(\phi(\mathbf{x}, 0), \phi(\mathbf{x}, 1)\right) = \int_{0}^1 \| v(\mathbf{x}, t) \|_L dt, 
\end{align}
dependent upon the choice of the linear operator, $L$, and
$v$ is the diffeomorphism-generating velocity field, 
\begin{align}
  v\left(\phi(\mathbf{x}, t), t \right) = \frac{d\phi(\mathbf{x}, t)}{dt},\,\,\, \phi(\mathbf{x}, 0) = \mathbf{x}.
\end{align}
$\Pi$ is the choice of similarity metric, often cross-correlation \cite{Avants2008a}, calculated in the 
virtual domain midway between each individual image and the current estimate of the template.

With initial assignment of $\left\{\left(\phi^m_1, \phi^m_2\right)\right\}$ and $\psi(\mathbf{x})$ 
to identity, iterative optimization
involves estimating the pairwise transformations, estimation of the optimal template appearance, and 
updating of $\psi(\mathbf{x})$ by averaging the current estimate of $\left\{\phi_1^m\right\}$.  Additional details are given in \cite{Avants2010}.  
%For the interested reader, a set of scripts has been created and is distributed with the ANTs library for facilitating template creation.

\subsection{Anatomically-Based Population Normalization}

An example of our proposed workflow applied to anatomically-based population normalization prior to TBSS analysis  is illustrated in Fig. \ref{fig:workflow}.  Instead of direct FA-to-FA registration, our ANTs-based modification can be described as follows:

\begin{enumerate}
  \item Build the anatomical template from  the population sample or sample subset using SyGN as described in
  the previous section.
  \item If only using a sample subset for template creation, register the remaining
        anatomical data to the template and save the resulting transformation for each         
        subject indexed by $i$ (i.e. $\mathcal{T}^i_{template}$).
  \item Find the optimal transformation from each
        subject's FA to the anatomical template:
  \begin{enumerate}
  \item For each anatomical image, segment the white matter (in ANTs, one can use N4 bias correction \cite{Tustison2010} and Atropos $n$-tissue segmentation \cite{Avants2011a}).
  \item Rigidly transform each subject's average DWI to the bias-corrected anatomical
        image ($\mathcal{R}^i_{dwi}$).
  \item Perform distortion correction on the FA to anatomical mapping 
        by localized nonrigid registration
        of rigidly transformed FA map ($=\mathcal{R}^i_{dwi} \mathrm{FA}$) using
        the white matter mask obtained in step 3(a) ($\mathcal{T}^i_{FA}$).
  \item For each subject, concatenate the transforms which maps each
        subject's FA to the template ($\mathcal{T}^i_{total} = \mathcal{T}^i_{template} \circ 
        \mathcal{T}^i_{FA} \circ \mathcal{R}^i_{dwi} \mathrm{FA}$).
  \item Warp each subject's FA or MD map to the template using $\mathcal{T}^i_{total}$.
  \end{enumerate}      
%  \item Perform the remaining portions of the standard TBSS pipeline:
%    \begin{enumerate}
%      \item Create the mean FA image from all template-aligned FA images.
%      \item Produce the white matter skeleton from the mean FA image.
%      \item Create skeleton distance map and project all FA data onto the skeleton.
%      \item Run the statistical analysis.
%    \end{enumerate}
\end{enumerate}

\subsection{Imaging Data}

Tensorial data associated with each of the following data sets were reconstructed from the diffusion weighted sequences using Camino%
\footnote{
http://camino.org.uk/
}---an open source toolkit for diffusion MRI processing and analysis \cite{Cook2006} in combination with ANTs-based registration for motion correction of the DTI sequence.

@@

The TBI data used in this study is part of a larger effort investigating the relationship between various neuroimaging indices and cognitive and functional abilities in long-term survivors of TBI (principal investigator: John Whyte). A more detailed data description can be found in \cite{Avants2008}. The following is a brief description relevant to our particular study.  
17 controls and 16 patients with TBI were used for the analysis presented in this
work.  Each patient had a history of non-penetrating traumatic brain injury 
of at least moderate severity defined by significant and well-documented
loss or alteration of consciousness following injury in addition to meeting
several other exclusionary criteria.  The healthy volunteers were matched in terms of age, gender, ethnicity, handedness, and
years of education.
High resolution T1-weighted anatomic images were obtained using 3D MP-RAGE 
imaging sequence using the following acquisition parameters: TR = 1620 ms, 
TI = 950 ms, TE = 3 ms, flip angle = 15$^\circ$, 160 contiguous slices of 
1.0 mm thickness, FOV = 192 $\times$ 256 mm$^2$, matrix = 192 $\times$ 256, 
1NEX with a scan time of 6 minutes, and voxel size = 1 mm$^3$.  30-directional
DTI images were also obtained.

@@

A patient template and a control template were  constructed 
from the T1-weighted images of the two groups.  These two 
templates were then used to create a third common template.  
To compare with TBSS normalization, the common template was
registered to the MNI152 template.  Thus, the transformation
which takes the FA image of an individual subject to the FMRIB58
template is the composition of transforms: 
subject FA $\rightarrow$ subject T1 $\rightarrow$ group T1 template $\rightarrow$ 
common T1 template $\rightarrow$ MNI152 (FMRIB58) template.
We evaluated this strategy relative to direct FA-to-FA
ANTs registration with the common similarity metrics used in
the simulated data example described earlier.
Standard TBSS alignment was also performed.

Statistical power curves (one-tailed, $\alpha = 0.95$)
are shown in Fig. \ref{fig:tbi_testing}.
Similar to previous findings with the simulated data, the SSD and 
Demons metric show elevated statistical power using the Student's 
$t$-test over the other alignment protocols which all exhibit similar 
strength.  However, this discrepancy decreases significantly with the 
nonparametric testing.  The Demons and SSD power decreases while the others
remain fairly similar.  Interestingly, the ANTs template-based approach
trends towards better performance relative to the remaining 3 strategies.
It should be noted that although TBSS uses
the SSD metric, the fixed and moving images are smoothed and subsampled
even at the highest resolution level which substantially decreases the local effect
of the metric.

@@

The CDF of the voxelwise FA coefficient of variation of the aligned
images is shown for each case in Figure \ref{fig:tbi_cov}.  This is
very much related to earlier findings in that strategies evincing
greater alignment, as quantified by the coefficient of variation,
will trend towards smaller variance thus exhibiting a left-shifted
CDF.  Although direct FA-to-FA registration using ANTs with common
similarity metrics gives ``better alignment'' such alignment is 
produced at a cost of significant type 1 errors.  Common subsampling and
smoothing strategies and local neighborhood metrics such as CC and MI reduce the 
Type 1 error problem (as evidenced in Fig. \ref{fig:tbi_testing}) 
but also show a decrease in alignment.  This is further supported
by the overlap measures \cite{Crum2006} given in Table \ref{table:lom}.
For each alignment strategy, we thresholded the derived mean FA image (FA $
\geq$ 0.2) and compared it with white matter mask of the MNI152 template
segmented using Atropos \cite{Avants2011a}.  The template-based
strategy showed the best overall overlap with the white matter MNI152
segmentation.

@@

Relative performance is quantified in the plots produced in Fig. \ref{fig:NKIplots}. 
The mean FA image derived from the standard TBSS approach was thresholded at FA $\geq 0.2$. 
 This binary mask obtained in the NKI cohort provided the standard group mask for 
 fair comparisons for all evaluations.    For all FMRIB58-aligned images the coefficient of 
 variation (CoV) was calculated in a voxel-wise fashion within the mask.  Intuitively, 
 one would expect a smaller variance across better aligned sets of voxel values thus 
 producing a lower CoV for a given mean value.  By calculating the cumulative distribution 
 function (CDF) of the set of CoV values within the mask, quantitative assessment of alignment performance can be visualized.  
% In addition to producing CDF plots for voxels within the entire brain mask, we separated the brain into inner and outer sections to investigate the alignment difference between these two regions.  This division was accomplished by applying a distance transform \cite{Maurer2003} to the FSL-provided MNI152 brain mask and thresholding the result such that the outer 30 mm form the outer mask and the subtracted binary image forms the inner mask.  Note that only those voxels that were also within the thresholded FA mask were considered in the inner/outer analysis.

@@

>>>>

After creation of the simulated data set, we performed voxelwise testing (both $t$-testing
and Wilcoxon rank-sum testing, one-tailed, $\alpha = 0.95$) with false discovery
rate correction within the white matter to get ``true'' cumulative distribution functions (CDFs).  The CDF vertical axis shows the cumulative number of voxels with corrected p-values at or below a given significance level (horizontal axis) and thus may be used as a surrogate measure for spatial sensitivity.  From here, we denote these graphs as "statistical significance curves."  These curves are plotted in black in Fig. \ref{fig:simulated_testing}.  To illustrate the 
effect of similarity metric on statistical significance, we performed ANTs registration \cite{Avants2011} of each subject to the template
(Fig. \ref{fig:simulated_data}(b)) using cross correlation (CC), mutual information (MI), 
Demons \cite{Thirion1998}, and sum of squared differences (SSD). A representative deformed image
using the SSD metric and its corresponding deformed grid is given in 
Fig. \ref{fig:simulated_data_warped}. 
The resulting statistical significance curves are plotted with the true significance curves in Fig. 
\ref{fig:simulated_testing}.

@@

\subsection{Anatomical Image Template Construction}
In general, we normalize images to to a standard coordinate system to
reduce intersubject variability in population studies.  Various
approaches exist for determining the normalized space such as selection
of a pre-existing template based on a single subject, e.g. the Talairach
atlas \cite{Talairach1988}), or a publicly available averaged group of
subjects, e.g. the MNI \cite{Collins1994} or ICBM \cite{Mazziotta1995}
templates.  One challenge with standard templates is that they may inadvertantly bias one's results by enabling better normalization of subjects to which the template is more similar.  This issue is exacerbated when dealing with populations that have high variance (e.g. due to disease) and/or when one's normalization method is low-dimensional (not flexible enough to capture large shape differences).

Population-specific templates (or optimal templates) alleviate some of
these issues by deriving a most representative image from the population
\cite{FIXME}.  Large deformation registration algorithms also reduce
this confound by being less sensitive to the deformation distance
between subject and target.  Some approaches combine both advantages,
for instance, the diffeomorphic approach of Joshi et al. who employ the
SSD metric and a shape distance to bring the subject group of images
into alignment \cite{Joshi2004}.  Variants
include extension to multiple modalities \cite{Lorenzen2006} and small deformations
\cite{Geng2009}.  These approaches iteratively minimize group difference in ``congealing''
towards a representative image template \cite{Learned-Miller2006}.

In contrast, Avants et al. explicitly model the geometric component of the 
normalized space during optimization.  Coupling the intrinsic symmetry of 
SyN pairwise registration \cite{Avants2011} and an
optimized sharpening/averaging of the template appearance, Symmetric Group
Normalization (SyGN) is a powerful framework for producing optimal population-specific
templates \cite{Avants2010} with arbitrary similarity metric choice. Given a set of representative images, 
$\{I_1, I_2, \ldots, I_M\}$, optimization involves finding the set of paired
diffeomorphic transformations, $\left\{\left(\phi^1_1, \phi^1_2\right), 
\left(\phi^2_1, \phi^2_2\right), \ldots, \left(\phi^M_1, \phi^M_2\right) \right\}$,
the optimal template appearance, $J^*$, and corresponding coordinate system, $\psi(\mathbf{x})$,
which minimize the following cost function:
\begin{align}
  \sum_{m=1}^M \left[
    D\left( \psi(\mathbf{x}), \phi^m_1(\mathbf{x}, 1) \right) + 
    \Pi \left( I_m\left(\phi^m_2(\mathbf{x}, 0.5) \right), J^*\left(\phi^m_1(\mathbf{x}, 0.5) \right) \right)
    \right]
\end{align}
where $D$ is the diffeomorphic shape distance, 
\begin{align}
  D\left(\phi(\mathbf{x}, 0), \phi(\mathbf{x}, 1)\right) = \int_{0}^1 \| v(\mathbf{x}, t) \|_L dt, 
\end{align}
dependent upon the choice of the linear operator, $L$, and
$v$ is the diffeomorphism-generating velocity field, 
\begin{align}
  v\left(\phi(\mathbf{x}, t), t \right) = \frac{d\phi(\mathbf{x}, t)}{dt},\,\,\, \phi(\mathbf{x}, 0) = \mathbf{x}.
\end{align}
$\Pi$ is the choice of similarity metric, often cross-correlation \cite{Avants2008a}, calculated in the 
virtual domain midway between each individual image and the current estimate of the template.

With initial assignment of $\left\{\left(\phi^m_1, \phi^m_2\right)\right\}$ and $\psi(\mathbf{x})$ 
to identity, iterative optimization
involves estimating the pairwise transformations, estimation of the optimal template appearance, and 
updating $\psi(\mathbf{x})$ by averaging the current estimate of $\left\{\phi_1^m\right\}$.  Additional details are given in \cite{Avants2010}.  
%For the interested reader, a set of scripts has been created and is distributed with the ANTs library for facilitating template creation.

\subsection{Anatomically-Based Population Normalization}
We now detail a standard approach that uses SyGN and intra-subject inter-modality mapping to provide an unbiased strategy for FA normalization.
An example of our proposed workflow applied to anatomically-based population normalization prior to FA analysis is illustrated in Fig. \ref{fig:workflow}.  Instead of direct FA-to-FA registration, our ANTs-based modification can be described as follows:

\begin{enumerate}
  \item Build the anatomical template from  the population sample or sample subset using SyGN as described in
  the previous section.
  \item If only using a sample subset for template creation, register the remaining
        anatomical data to the template and save the resulting transformation for each         
        subject indexed by $i$ (i.e. $\mathcal{T}^i_{template}$).
  \item Find the optimal transformation from each
        subject's FA to the anatomical template:
  \begin{enumerate}
  \item For each anatomical image, segment the white matter (in ANTs, one can use N4 bias correction \cite{Tustison2010} and Atropos $n$-tissue segmentation \cite{Avants2011a}).
  \item Rigidly transform each subject's average DWI to the bias-corrected anatomical image ($\mathcal{R}^i_{dwi}$).
  \item Perform distortion correction on the FA to anatomical mapping 
        by localized nonrigid registration
        of rigidly transformed FA map ($=\mathcal{R}^i_{dwi} \mathrm{FA}$) using
        the white matter mask obtained in step 3(a) ($\mathcal{T}^i_{FA}$).
  \item For each subject, concatenate the transforms which maps each
        subject's FA to the template ($\mathcal{T}^i_{total} = \mathcal{T}^i_{template} \circ 
        \mathcal{T}^i_{FA} \circ \mathcal{R}^i_{dwi} \mathrm{FA}$).
  \item Warp each subject's FA map to the template using $\mathcal{T}^i_{total}$.  Equivalently, one could warp the mean diffusion (MD), axial diffusion (AD) or any other scalar derivable from DTI to the template.  One other detail is that we prefer to warp the subject's DTI to the template and then, in template space, derive the scalar images of interest.  
  \end{enumerate}      
%  \item Perform the remaining portions of the standard TBSS pipeline:
%    \begin{enumerate}
%      \item Create the mean FA image from all template-aligned FA images.
%      \item Produce the white matter skeleton from the mean FA image.
%      \item Create skeleton distance map and project all FA data onto the skeleton.
%      \item Run the statistical analysis.
%    \end{enumerate}
\end{enumerate}
The next section compares this framework to FA-based normalization strategies with respect to both a patient-control study and a study of gender and age effects in a control population.

\subsection{Imaging Data}
Diffusion tensor data associated with each of the following data sets were reconstructed from the diffusion weighted sequences using Camino%
\footnote{
http://camino.org.uk/
}---an open source toolkit for diffusion MRI processing and analysis \cite{Cook2006} in combination with ANTs-based registration for motion correction of the DTI sequence.

@@

The TBI data used in this study is part of a larger effort investigating the relationship between various neuroimaging indices and cognitive and functional abilities in long-term survivors of TBI (principal investigator: John Whyte). A more detailed data description can be found in \cite{Avants2008}. The following is a brief description relevant to our particular study.  
17 controls and 16 patients with TBI were used for the analysis presented in this work.  Each patient had a history of non-penetrating traumatic brain injury 
of at least moderate severity defined by significant and well-documented
loss or alteration of consciousness following injury in addition to meeting
several other exclusionary criteria.  The healthy volunteers were matched in terms of age, gender, ethnicity, handedness, and years of education.
High resolution T1-weighted anatomic images were obtained using a 3D MP-RAGE 
imaging sequence with the following acquisition parameters: TR = 1620 ms, 
TI = 950 ms, TE = 3 ms, flip angle = 15$^\circ$, 160 contiguous slices of 
1.0 mm thickness, FOV = 192 $\times$ 256 mm$^2$, matrix = 192 $\times$ 256, 
1NEX with a scan time of 6 minutes, and voxel size = 1 mm$^3$.  30-directional
DTI images were also obtained. 

@@

We constructed a patient template and a control template from the T1-weighted images of the two groups.  These two 
templates were then used to create a third common template.  
To compare with TBSS normalization, the common template was
registered to the MNI152 template.  Thus, the transformation
which takes the FA image of an individual subject to the FMRIB58
template is the composition of transforms: 
subject FA $\rightarrow$ subject T1 $\rightarrow$ group T1 template $\rightarrow$ 
common T1 template $\rightarrow$ MNI152 (FMRIB58) template.
We evaluated this strategy relative to direct FA-to-FA
ANTs registration with the common similarity metrics used in
the simulated data example described earlier.
Standard TBSS alignment was also performed.

Cumulative distribution functions (one-tailed, $\alpha = 0.95$)
are shown in Fig. \ref{fig:tbi_testing}.
Similar to previous findings with the simulated data, the SSD and 
Demons metric show elevated statistical power using the Student's 
$t$-test over the other alignment protocols which all exhibit similar 
strength.  However, this discrepancy decreases significantly with the 
nonparametric testing.  The Demons and SSD power decreases while the others
remain fairly similar.  Interestingly, the ANTs template-based approach
trends towards better performance relative to the remaining 3 strategies.
It should be noted that although TBSS uses the SSD metric, the fixed and moving images are smoothed and subsampled even at the highest resolution level which substantially decreases the local effect of the metric.

@@

The CDF of the voxelwise FA coefficient of variation {\textcolor{red}{ FIXME define coefficient of variation and explain what it means --- how does it relate to variance?}} of the aligned
images is shown for each case in Figure \ref{fig:tbi_cov}.  This is
very much related to earlier findings in that strategies evincing
greater alignment, as quantified by the coefficient of variation,
will trend towards smaller variance thus exhibiting a left-shifted
CDF.  Although direct FA-to-FA registration using ANTs with common
similarity metrics gives ``better alignment'' such alignment is 
produced at a cost of significant type 1 errors.  Common subsampling and
smoothing strategies and local neighborhood metrics such as CC and MI reduce the 
Type 1 error problem (as evidenced in Fig. \ref{fig:tbi_testing}) 
but also show a decrease in alignment.  This is further supported
by the overlap measures \cite{Crum2006} given in Table \ref{table:lom}.
For each alignment strategy, we thresholded the derived mean FA image (FA $
\geq$ 0.2) and compared it with white matter mask of the MNI152 template
segmented using Atropos \cite{Avants2011a}.  The template-based
strategy showed the best overall overlap with the white matter MNI152
segmentation.

@@

Relative performance is quantified in the plots produced in Fig. \ref{fig:NKIplots}. 
The mean FA image derived from the standard TBSS approach was thresholded at FA $\geq 0.2$. 
 This binary mask obtained in the NKI cohort provided the standard group mask for 
 fair comparisons for all evaluations.    For all FMRIB58-aligned images the coefficient of 
 variation (CoV) was calculated in a voxel-wise fashion within the mask.  Intuitively, 
 one would expect a smaller variance across better aligned sets of voxel values thus 
 producing a lower CoV for a given mean value.  By calculating the CDF of the set of CoV values within the mask, quantitative assessment of alignment performance can be visualized.  
% In addition to producing CDF plots for voxels within the entire brain mask, we separated the brain into inner and outer sections to investigate the alignment difference between these two regions.  This division was accomplished by applying a distance transform \cite{Maurer2003} to the FSL-provided MNI152 brain mask and thresholding the result such that the outer 30 mm form the outer mask and the subtracted binary image forms the inner mask.  Note that only those voxels that were also within the thresholded FA mask were considered in the inner/outer analysis.

@@

\subsection{Discussion} Prior evaluation work using anatomically labeled
data \cite{bunch_of_stuff} indicates that mutual information,
cross-correlation and the SSD/Demons metric are all capable of producing
high quality anatomical alignment.  All of this work, though, compares
the quality of alignment at a relatively coarse scale of major gyri,
lobes and regions.  At the voxel level, it is nearly impossible to
determine the ground truth correspondence.  Indeed, there is no reason
to believe that subtle differences between a set of alignment strategies
(induced, in the experiments of this paper, by changing the similarity
metrics used in image registration) that all apparently work well should
be considered significant.  This work, however, highlights a dramatic impact of similarity metric choice on detection power in template-based FA studies.  Our contention is that this dramatic "improvement" in detection power is not due to better anatomical alignment.  Rather, it is a result of circularity/non-independence of the normalization and statistical estimation strategy.  Consequently, we recommend that future work should take greater care when pairing the normalization strategy with the statistical framework.  Furthermore, we recommend that researchers should diligently seek to maintain independence between these two critical stages of a population study.  That is, {\textcolor{red}{{\em the features that drive the minimization of a similarity metric should be independent of the features that will be used in hypothesis testing.)}}}
